---
title: "How to obtain a typology of projects"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{how-to-obtain-a-typology-of-projects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
# library(goodpracticestools)
pkgload::load_all()
```

## How to explore the variability of the projects

The data was prepared using the `prepare_data()` function. See the article [How to prepare data for statistical analysis](https://promotionsante.github.io/goodpracticestools/articles/how-to-prepare-data-for-statistical-analysis.html) for more details.

```{r}
data("data_fr")
```

The data are analyzed using **Multiple Correspondence Analysis** (MCA), a statistical method that helps explore and visualize relationships between several categorical variables. 

In this analysis, the active variables are as follows: 

- the A/B/C/D columns,
- the level column, 
- the theme columns, 
- the target groups columns,  
- and the settings columns. 

MCA allows for the identification of underlying structures and associations between these variables, providing a clear view of the links and patterns present in the data. 

Following the MCA, a **Hierarchical Clustering on Principal Components** (HCPC) is performed to further group similar observations and enhance the interpretation of the results.

The `get_clusters()` function realizes the analysis:

```{r}
res_analysis <- get_clusters(
  data = data_fr
)
```

## How to plot the clusters of projects

The `plot_clusters()` function then displays the factorial plane from the MCA with the representation of the clusters:

```{r, fig.width=6, fig.height=4, fig.align='center'}
plot_clusters(
  res_analysis = res_analysis
)
```

The German version is also available:

```{r}
data("data_raw_de")
```

```{r, fig.width=6, fig.height=4, fig.align='center'}
plot_clusters(
  res_analysis = res_analysis, 
  data_raw_de = data_raw_de,
  language = "de"
)
```

## How to interpret the clusters of projects


