---
title: "How to prepare data for statistical analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{how-to-prepare-data-for-statistical-analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(goodpracticestools)
library(dplyr)
library(stringr)
library(knitr)
```

## Raw data

The raw FR example data is available in the `"data_raw_fr"` dataset:

```{r}
data("data_raw_fr")
head(data_raw_fr) |> 
  mutate(
    across(
      everything(), 
      ~ str_trunc(.x, 20)
    )
  ) |> 
  kable()
```

The DE version is available in the `"data_raw_de"` dataset:

```{r}
data("data_raw_de")
head(data_raw_de) |> 
  mutate(
    across(
      everything(), 
      ~ str_trunc(.x, 20)
    )
  ) |> 
  kable()
```

## How to prepare data for statistical analysis

Only **French data** is used for the statistical analysis (see ADR X).

The preparation steps are as follows:

- Verify that the expected columns are present
- Retain only the mandatory columns
- Clean column names and use more explicit ones for certain columns
- For the `Thème`, `Groupe cible`, and `Setting` columns, which contain multiple values per cell, convert them into disjunctive columns
- Replace missing values (`NA`) in columns I, II, III and A, B, C, D.

These steps are implemented in the function `prepare_data()`:

```{r}
data_fr <- prepare_data(
  data = data_raw_fr
)
```

The result is as follows:

```{r}
data_fr |> 
  select(
    fiche_d_informations_id,
    nom,
    i_enfants_adolescents,
    ii_adultes,
    iii_personnes_agees,
    a_enfants_adolescents_nutrition_activite_physique,
    b_personnes_agees_nutrition_activite_physique,
    c_enfants_adolescents_sante_psychique,
    d_personnes_agees_sante_psychique, 
    starts_with("theme"), 
    starts_with("groupe_cible"),
    starts_with("setting")
  ) |> 
  head() |> 
  kable()
```
