---
title: "How to explore the projects graphically"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{how-to-explore-the-projects-graphically}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(goodpracticestools)
pkgload::load_all()
```

## Prepared data 

The data was prepared using the `prepare_data()` function. See the article **"How to prepare data for statistical analysis"** for more details.

```{r}
data("data_fr")
```

## How to explore the distribution of projects by type A / B / C / D

The projects are linked to one or more of these types:

A - Nutrition focus for children/teenagers
B - Nutrition focus for the elderly
C - Mental health focus for children/teenagers
D - Mental health focus for the elderly

The `plot_distrib_type()` function displays the distribution of observations across one of these types.

```{r}
plot_distrib_type(
  data = data_fr
)
```


**Note: Some projects are associated with more than one type. Others are not associated with any type.**
